PAGAI

### 2012-05-18 papers/TAPAS2012/pagai.tex
citation smtlib2

\usepackage{amsmath}
\usepackage{mathcomp,amsfonts,amssymb,MnSymbol}
\usepackage[authoryear]{natbib}
\usepackage[mathscr]{euscript}
\usepackage{algorithmic,algorithm}
\usepackage{graphicx}
\usepackage{color}

@@

\newcommand{\Nat}{{\mathbb N}}
\newcommand{\Real}{{\mathbb R}}
\def\lastname{Henry}
\begin{document}
\begin{frontmatter}
  \title{PAGAI} 
  \author{Julien Henry \thanksref{imag.fr}}
  \address{Universit\'e Joseph Fourier, VERIMAG\\
    Grenoble, France} 
	\author{David Monniaux\thanksref{imag.fr}}
  \address{CNRS, VERIMAG\\
    Grenoble, France} 
	\author{Matthieu Moy\thanksref{grenoble-inp.fr}}
  \address{Grenoble-INP, VERIMAG\\
    Grenoble, France}

    \thanks[imag.fr]{Email:
    \href{First Name.Last Name@imag.fr} {\texttt{\normalshape
        First Name.Last Name@imag.fr}}} 
    \thanks[grenoble-inp.fr]{Email:
    \href{Matthieu.Moy@grenoble-inp.fr} {\texttt{\normalshape
        Matthieu.Moy@grenoble-inp.fr}}} 
\begin{abstract} 
	We present design and implementation of PAGAI, a new static analyzer 
	working over the LLVM compiler infrastructure, that computes inductive
	invariants on the numerical variables of the program.
	PAGAI implements various state-of-the-art techniques combining Abstract
	Interpretation and Decision Procedures (SMT-solving), and offers
	several abstract domains.
	We thus can compare in time and precision the various combinations of
	techniques and abstract domains. We conducted extensive experiments for
	comparing these techniques on several benchmarks and GNU programs.
\end{abstract}
\begin{keyword}
	Static Analysis, Program Verification, Abstract Interpretation, Decision
	Procedure, Satisfiability Modulo Theories.
\end{keyword}
\end{frontmatter}
\section{Introduction}\label{intro}

This paper introduces PAGAI, a new tool for static analysis, that
computes numerical invariants at the different control points of a program.
This tool uses the internal representation of LLVM\citep{LLVM_langref,Lattner:2004:LCF:977395.977673},
which is a target for several industrial-strengh compilers, most notably Clang (supporting C and
C++) and llvm-gcc (supporting C, C++, Fortran and Ada).
Several other verification tools already use the LLVM framework, such as
Calysto, KLEE, LAV, LLBMC.

Our tool is dedicated to experiment with various combination of analysis techniques
by abstract interpretation.
Indeed, depending on the iteration strategy, the choice of the abstract domain,
etc, precision and cost of the analysis hugely vary. Our platform allows to
compare various state-of-the-art techniques and abstract domains on real life
programs, such as GNU projects.

\section{Motivating Example}

These techniques make a precise analysis of the paths inside the program

@@

	Abstract domains are provided by the APRON library \citep{DBLP:conf/cav/JeannetM09}, and include convex polyhedra (from the builtin Polka ``PK'' library), octagons, intervals, and linear congruences.
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}
through their C API, and can also operate with any SMT-solver supporting the
SMT-Lib 2 standard \cite{BarST-SMTLIB} through a pipe.

@@

\phantomsection\addcontentsline{toc}{section}{References} 
	\bibliographystyle{plainnat}
\bibliography{pagai}
\end{document}

>>>>

\usepackage{amsmath}
\usepackage{mathcomp,amsfonts,amssymb,MnSymbol}
\usepackage{natbib}
\usepackage[mathscr]{euscript}
\usepackage{algorithmic,algorithm}
\usepackage{graphicx}
\usepackage{color}

@@

\newcommand{\Nat}{{\mathbb N}}
\newcommand{\Real}{{\mathbb R}}
\def\lastname{Henry}
\begin{document}
\begin{frontmatter}
  \title{PAGAI} 
  \author{Julien Henry \thanksref{imag.fr}}
  \address{VERIMAG\\ Universit\'e Joseph Fourier\\
    Grenoble, France} 
	\author{David Monniaux\thanksref{imag.fr}}
  \address{VERIMAG\\CNRS\\
    Grenoble, France} 
	\author{Matthieu Moy\thanksref{grenoble-inp.fr}}
  \address{VERIMAG\\Grenoble-INP\\
    Grenoble, France}

    \thanks[imag.fr]{Email:
    \href{First Name.Last Name@imag.fr} {\texttt{\normalshape
        First Name.Last Name@imag.fr}}} 
    \thanks[grenoble-inp.fr]{Email:
    \href{Matthieu.Moy@grenoble-inp.fr} {\texttt{\normalshape
        Matthieu.Moy@grenoble-inp.fr}}} 
\begin{abstract} 
	We present design and implementation of PAGAI, a new static analyzer 
	working over the LLVM compiler infrastructure, that computes inductive
	invariants on the numerical variables of the program.
	PAGAI implements various state-of-the-art techniques combining Abstract
	Interpretation and Decision Procedures (SMT-solving), and offers
	several abstract domains.
	We thus can compare in time and precision the various combinations of
	techniques and abstract domains. We conducted extensive experiments for
	comparing these techniques on several benchmarks and GNU programs.
\end{abstract}
\begin{keyword}
  Please list keywords from your paper here, separated by commas.
\end{keyword}
\end{frontmatter}
\section{Introduction}\label{intro}
Introduction

@@

%\MM{On peut peut-être citer le nom de l'outil (on garde PAGAI ?) ici.
%  L'intérêt d'avoir un nom, c'est que les gens peuvent en parler plus
%  facilement, et c'est plus facile de retrouver le papier origine d'un
%  outil quand il cite son nom}
%\DM{Dans la version finale, oui, mais pas dans une soumission anonymisée... suffit de Googlifier pagai sur imag.fr}
%
Our tool operates over LLVM bitcode \citep{LLVM_langref,Lattner:2004:LCF:977395.977673}, which is a target for several compilers, most notably Clang (supporting C and C++) and llvm-gcc (supporting C, C++, Fortran and Ada).
Abstract domains are provided by the APRON library \citep{DBLP:conf/cav/JeannetM09}, and include convex polyhedra (from the builtin Polka ``PK'' library), octagons, intervals, and linear congruences.
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}
through their C API, and can also operate with any SMT-solver supporting the
SMT-Lib 2 standard \cite{BarST-SMTLIB,BarST-SMT-10} through a pipe.

@@

% Cas a probleme:
% Initialisation (x,y) à {(1,0), (0,1)}
% puis boucle: si y = 0 alors x++
% fait un polyèdre qui finit par perdre y <= 1 et x >= 0

%\appendix
%\section{Appendix Title}

%This is the text of the appendix, if you need one.

%\acks

% Acknowledgments, if needed.

% We recommend abbrvnat bibliography style.

\phantomsection\addcontentsline{toc}{section}{References} 
\bibliographystyle{plain}
\bibliography{pagai}
\end{document}
